Detection of defects in additive manufacturing from a single x-ray projection using the empirical null filter

### 2019-07-01 reports/paper1/paper.tex
Revise paper

>>>>

In the experiment with the test sample, the angle was chosen to distinguish the designed voids. For general AM products, finding a suitable singular projection angle can be difficult. This problem can be tackled by conducting defect detection on a small number of different angular projections independently to pick up defects hidden behind another.
